---
title: "Quality of life indicators"
author: "Maripaz Venegas"
date: "2024-06-21"
output: html_document
---

# Quality of life indicators - natural and living environment
https://ec.europa.eu/eurostat/statistics-explained/index.php?title=Quality_of_life_indicators_-_natural_and_living_environment

## Figure 1
Population reporting exposure to pollution, grime or other environmental problems, EU, 2011-2020
https://ec.europa.eu/eurostat/statistics-explained/index.php?title=File:Population_reporting_exposure_to_pollution,_grime_or_other_environmental_problems,_EU_(%C2%B9),_2011-2020_(%25).png
```{r}
#Joseph
```


## Figure 2
Population reporting exposure to pollution, grime or other environmental problems, by income situation, 2020
https://ec.europa.eu/eurostat/statistics-explained/index.php?title=File:Population_reporting_exposure_to_pollution,_grime_or_other_environmental_problems,_by_income_situation,_2020_(%25)_.png
```{r}
#Joseph
```

## Figure 3
Population reporting exposure to pollution, grime or other environmental problems, by degree of urbanisation, 2020
https://ec.europa.eu/eurostat/statistics-explained/index.php?title=File:Population_reporting_exposure_to_pollution,_grime_or_other_environmental_problems,_by_degree_of_urbanisation,_2020_(%25)_.png
```{r}
#Joseph
```

## Figure 4
Population reporting noise from neighbours or from the street, EU, 2011-2020
https://ec.europa.eu/eurostat/statistics-explained/index.php?title=File:Population_reporting_noise_from_neighbours_or_from_the_street,_EU_(%C2%B9)_,_2011-2020_(%25).png
```{r}
#Maripaz
```

## Figure 5
Population reporting noise from neighbours or from the street, by income situation, 2020
https://ec.europa.eu/eurostat/statistics-explained/index.php?title=File:Population_reporting_noise_from_neighbours_or_from_the_street,_by_income_situation,_2020_(%25).png
```{r}
#Maripaz
```

## Figure 6
Population reporting noise from neighbours or from the street, by degree of urbanisation, 2020
https://ec.europa.eu/eurostat/statistics-explained/index.php?title=File:Population_reporting_noise_from_neighbours_or_from_the_street,_by_degree_of_urbanisation,_2020_(%25).png
```{r}
#Wendy
```
